Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Fix phrasing
Fix position of appendix figures
Switch figure - need to rename them again
Fix table legend and table refs

%\subsubsection{Ground-level ozone observations}
%\label{subsubsec:ebas}
\begin{figure}[t]
  %\includegraphics[width=8.3cm]{station_map_fennoscandia}
  \includegraphics[width=8.3cm]{fig03}
  \caption{Cap of the North. Locations of past and present (end of 2018) ozone observation sites in northern Fennoscandia were used in this study. For more details see Tab.~\ref{tab:ebas_obs}. The same color coding for each station as displayed herein will be used in all the following figures.}
  \label{fig:station_map_fennoscandia}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
  \includegraphics[width=8.3cm]{fig09}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

Another important factor for ozone exposure metrics is the timing and length of the GS. Start ($A_\text{start}$) and end ($A_\text{end}$) of GS for each PFT are given in units of \unit{doy} (Tab.~\ref{tab:sensitivity_tests_gs}) and estimated as follows. Evergreen needle leaf trees show photosynthetic activity already at low temperatures \citep{TP:Wallin2013, TB:Kolari2007}. We use a MODIS (Aqua/Terra) retrieved net photosynthesis product for a $1\times 1\,\unit{km}$ patch centered at Svanhovd to determine $A_\text{start}$ and $A_\text{end}$. Net photosynthesis data can be approximated by a second order polynomial function (Fig.~\ref{fig:modis_Psn}). By calculating the roots of the fitted polynomial, we derive $A_\text{start} = 122\,\unit{doy}$ for 2018 and \unit{doy} 106 in 2019. $A_\text{end}$ amounts to \unit{doy} 261 and 274, respectively, and is the value used for all PFTs. The resulting growing season for coniferous trees in 2019 was one month longer then in 2018. For estimating $A_\text{start}$ of deciduous trees, we use the $5$ consecutive days above $5\,\unit{^\circ C}$ agricultural rule of thumb on gridded temperature data from SeNorge.no (Fig.~\ref{fig:greening_season_change_Svanvik}). We find 129 and 130, respectively. For both years, these dates coincident with the first snow-free day at the meteorological weather station at Øvre Neiden (Sør-Varanger, NOR) which is relatively close-by.
For comparison, we would get $A_\mathrm{start} = 100\,\unit{doy}$ and $A_\mathrm{end} = 307\,\unit{doy}$ from the latitude model typically used for localizing $\mathrm{DO_3SE}$. By comparison, the latitude model indicates about a $2\,\unit{month}$ longer growing season. Due to a lack of quantitative field observation, we assume a latency period of about $1\,\unit{month}$ after snow-melt for perennial grassland.

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig11}
  \caption{$\mathrm{DO_3SE}$ modeling results for $\mathrm{POD_1}$ with default parameterization (MM) and bespoke parameters for Svanhovd. Bespoke parameterizations include temperature response functions for subarctic, cold and light thresholds (PPFD0.8, PPFD1.2) at the end of a MM GS (lighter hue and dotted lines) and the estimated GS for Svanhovd (2018, 2019). (a) Deciduous tree; (b) coniferous tree; (c) perennial grassland. The dashed horizontal lines indicate critical levels defined in \citet{ICP:MappingManual2017,ESPR:Hayes2021} for each species, respectively.}
  \label{fig:pody_rel}
\end{figure}

@@

\appendixfigures  %% needs to be added in front of appendix figures
\begin{figure*}[t]
  \includegraphics[width=12cm]{figA1}
  \caption{Observed global irradiance at Svanvik. (a) Climatology (hourly maxima, mean, and minima); deviation from climatology (b) 2018; (c) 2019. The cyan lines indicate the $1\,\sigma$ level derived from climatology.}
  \label{fig:global_rad_clim}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{figA2}
  \caption{Probability densities and correlation coefficient for \chem{[O_3]} between different sites in northern Fennoscandia. Jergul/Karasjok is well correlated with Esrange, and Pallas. Svanvik displays highest correlation with Pallas. Note: The stripe at $26\,\unit{ppb}$ is an artifact from plotting. (a) Jergul/Karasjok--Esrange; (b) Jergul/Karasjok--Pallas; (c) Svanvik--Esrange; (d) Svanvik--Pallas.}
  \label{fig:density_distribution}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{figB1}
  \caption{Estimated $G_\mathrm{start}$ and $G_\mathrm{end}$ of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure}

>>>>

%\subsubsection{Ground-level ozone observations}
%\label{subsubsec:ebas}
\begin{figure}[t]
  %\includegraphics[width=8.3cm]{station_map_fennoscandia}
  \includegraphics[width=8.3cm]{fig03}
  \caption{Cap of the North. Locations of past and present (end of 2018) ozone observation sites in northern Fennoscandia were used in this study. For more details see Table~\ref{tab:ebas_obs}. The same color coding for each station as displayed herein will be used in all the following figures.}
  \label{fig:station_map_fennoscandia}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
  \includegraphics[width=8.3cm]{fig07fin}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

Another important factor for ozone exposure metrics is the timing and length of the GS. Start ($A_\text{start}$) and end ($A_\text{end}$) of GS for each PFT are given in units of \unit{doy} (Table~\ref{tab:sensitivity_tests_gs}) and estimated as follows. Evergreen needle leaf trees show photosynthetic activity already at low temperatures \citep{TP:Wallin2013, TB:Kolari2007}. We use a MODIS (Aqua/Terra) retrieved net photosynthesis product for a $1\times 1\,\unit{km}$ patch centered at Svanhovd to determine $A_\text{start}$ and $A_\text{end}$. Net photosynthesis data can be approximated by a second order polynomial function (Fig.~\ref{fig:modis_Psn}). By calculating the roots of the fitted polynomial, we derive $A_\text{start} = 122\,\unit{doy}$ for 2018 and \unit{doy} 106 in 2019. $A_\text{end}$ amounts to \unit{doy} 261 and 274, respectively. This value will be used for all PFTs alike. The resulting growing season for coniferous trees in 2019 was one month longer then in 2018. For estimating $A_\text{start}$ of deciduous trees, we use the $5$ consecutive days above $5\,\unit{^\circ C}$ agricultural rule of thumb on gridded temperature data from SeNorge.no (Fig.~\ref{fig:greening_season_change_Svanvik}). We find 129 and 130, respectively. For both years, these dates coincident with the first snow-free day at the meteorological weather station at Øvre Neiden (Sør-Varanger, NOR) which is relatively close-by.
For comparison, we would get $A_\mathrm{start} = 100\,\unit{doy}$ and $A_\mathrm{end} = 307\,\unit{doy}$ from the latitude model typically used for localizing $\mathrm{DO_3SE}$. By comparison, the latitude model indicates about a $2\,\unit{month}$ longer growing season. Due to a lack of quantitative field observation, we assume a latency period of about $1\,\unit{month}$ after snow-melt for perennial grassland.

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig11}
  \caption{$\mathrm{DO_3SE}$ modeling $\mathrm{POD_1}$ results for (a) deciduous trees, (b) coniferous trees, and (c) perennial grasslands at Svanhovd in 2018 (pink) and 2019 (purple). The results varied depending on parameterizations of temperature response functions (MM, Cold, and Subarctic, details in Table~\ref{tab:sensitivity_tests_temp}), growing season (MM (squares) or bespoke (circles), details in Table~\ref{tab:sensitivity_tests_gs}), light response functions (first, second and third point attached by a line are depicting the MM, PPFD0.8 and PPFD1.2, details in Table~\ref{tab:sensitivity_tests_light}), and the effect of taking SWP into account (filled symbols without and open symbols with effects of drought kept in the model). Critical levels for ozone damage \citet{ICP:MappingManual2017,ESPR:Hayes2021} are given as dashed horizontal lines. Note that the horizontal axis is only categorical..}
  \label{fig:pody_rel}
\end{figure}

DO3SE modelling POD1 results (Mills et al., 2017; Hayes et al., 2021) are given as dashed horizontal lines. Note that the horizontal axis is only categorical.

@@

\appendixfigures  %% needs to be added in front of appendix figures
\begin{figure}[th]
  \includegraphics[width=8.3cm]{figA1}
  \caption{Observed global irradiance at Svanvik. (a) Climatology (hourly maxima, mean, and minima); deviation from climatology (b) 2018; (c) 2019. The cyan lines indicate the $1\,\sigma$ level derived from climatology.}
  \label{fig:global_rad_clim}
\end{figure}

\begin{figure}[th]
  \includegraphics[width=8.3cm]{figA2}
  \caption{Probability densities and correlation coefficient for \chem{[O_3]} between different sites in northern Fennoscandia. Jergul/Karasjok is well correlated with Esrange, and Pallas. Svanvik displays highest correlation with Pallas. Note: The stripe at $26\,\unit{ppb}$ is an artifact from plotting. (a) Jergul/Karasjok--Esrange; (b) Jergul/Karasjok--Pallas; (c) Svanvik--Esrange; (d) Svanvik--Pallas.}
  \label{fig:density_distribution}
\end{figure}

@@

\begin{figure}[th]
  \includegraphics[width=8.3cm]{figB1}
  \caption{Estimated $G_\mathrm{start}$ and $G_\mathrm{end}$ of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure}
